### 2022-08-12 article.tex
Progress

The code that does the work in a computational experiment should
always be published together with a scholarly article.
For research to be reproducible, one ideally has access to
both the data used and the code.
In some fields, such as genetic epidemiology, the data is
sensitive, hence cannot be released,
yet there are methods being devised to run code on sensitive
data with assured privacy (\cite{zhang2016review,azencott2018machine}).

Code has additional useful information, similar to confidence intervals,
that allow a reader to gauge how much he/she trusts the results.
The most important way to determine the quality of code
is the amount of unit tests.
When following a set of best practices, such as DevOps, TDD, Agile,
writing unit tests is an essential 
part in writing code.
The amount of unit tests is an honest signal 
for code correctness (i.e. it does what it is supposed to do, as opposed
to 'it does something').
In academia, to uncover the truth, code correctness is essential.
To make a comparison with cell biologists, where working
sterile is essential to have the correct results,
unit tests allow a computational biologist to achieve the same.

>>>>

Code is paradata, as it is describes how the results are generated.
The part of a scholarly article that describes the experiment is metadata, 
as it describes what the code is thought to do.
The code that does the work in a computational experiment should
always be published together with a scholarly article,
as, if the paper and code differ, it is the code that generated the results.

For research to be reproducible, one ideally has access to
both the data used and the code.
In some fields, such as genetic epidemiology, the data is
sensitive, hence cannot be released,
yet there are methods being devised to run code on sensitive
data with assured privacy (\cite{zhang2016review,azencott2018machine}).

Code has additional useful information, similar to confidence intervals,
that allow a reader to gauge how much he/she trusts the results.
The most important way to determine the quality of code
is the amount of unit tests.
When following a set of best practices, such as DevOps, TDD, Agile,
writing unit tests is an essential 
part in writing code.
The amount of unit tests is an honest signal 
for code correctness (i.e. it does what it is supposed to do, as opposed
to 'it does something').
In academia, to uncover the truth, code correctness is essential,
similar to cell biologists working sterile to not contaminate their
cell cultures.
Unit tests are a vital practice for a computational biologist.
